Astr 513: Final Project

### 2016-05-08 Final_Project/ms.tex
Added plot commands and values
Added plot commands for more of the plots. Also added values in the
tables for the chains that are finished already. May rerun Rest wCDM
with priors if time, but mostly waiting for Rest LCDM with priors

\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distributions of parameters in the
      $\Lambda$CDM model. Uncertainties denote symmetrized 68\%
      confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distributions of parameters in the
    $w$CDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a $w$CDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_prior_bestfit}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $w$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_corner}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $\Lambda$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_corner}
\end{figure}
%

>>>>

\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & $0.315 \pm 0.002$      & $0.665 \pm 0.002$ \\
    Betoule et al. (no priors) & $0.30 \pm 0.03$      & $0.701 \pm 0.007$ \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & $0.5 \pm 0.3$      & $0.68 \pm 0.07$ \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distributions of parameters in the
      $\Lambda$CDM model. Uncertainties denote symmetrized 68\%
      confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & $0.290 \pm 0.002$                      & $0.664 \pm 0.002$     & $-0.830 \pm 0.007$     \\
    Betoule et al. (no priors) & $0.2 \pm 0.1$                      & $0.699 \pm 0.008$     & $-0.9 \pm 0.2$     \\
    Rest et al.                & $0.4 \pm 0.3$                      & $0.68 \pm 0.06$     & $-1.1 \pm 0.6$     \\
    Rest et al. (no priors)    & $0.5 \pm 0.3$                      & $0.68 \pm 0.07$    & $-0.4 \pm 0.5$     \\
    \Planck likelihood only    & $0.295 \pm 0.003$                      & $0.658 \pm 0.002$     & $-0.827 \pm 0.007$     \\
  \end{tabular}
  \caption {Posterior distributions of parameters in the
    $w$CDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \includegraphics[width=0.5\linewidth]{figures/rest_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data (left) and \citet{rest2014} data (right) including the
    \Planck priors for a $w$CDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_prior_bestfit}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $w$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_corner}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/rest_wcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/rest_wcdm_withpriors_corner.eps}
  \caption{Same as ~\autoref{fig:betoule_wcdm_corner} but with the \citet{rest2014} data.}
  \label{fig:rest_wcdm_corner}
\end{figure}
%
\EW{Wasn't sure where to put the \Planck only corner plot}
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/nosn_wcdm_corner.eps}
  \caption{Same as ~\autoref{fig:betoule_wcdm_corner} and ~\autoref{fig:rest_wcdm_corner}, but using only \Planck likelihoods without \sn{} data.}
  \label{fig:nosnia_wcdm_corner}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $\Lambda$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_corner}
\end{figure}
%
